Har en persons høyde innvirkning på lønnen?

### 2020-10-09 MSB105-Assignment-2-Katrine-Karl-Gunnar.Rmd
Geom smooth med gammel og ny variabel.

```{r geom_smooth, echo=False}
heightsPosInc <- subset(heights, income > 0)
ggplot(heightsPosInc, mapping = aes(x = height_cm, y = inntekt)) +
  scale_y_continuous(trans = scales::log_trans()) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')
```

>>>>

```{r heightsposinc-jitter-smooth, echo=False}
m5 <- ggplot(heights, mapping = aes(x = height_cm, y = inntekt)) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')

m6 <- ggplot(heights_liminc, mapping = aes(x = height_cm, y = inntekt)) +
  geom_point(position = "jitter") +
  geom_smooth(method = 'lm')

ggarrange(m5, m6)
```
